Kernel k-Groups via Hartigan's Method

### 2018-08-13 energy_clustering/pami18/energy_clustering.tex
pami update
pami

\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio]{gui2.png}}]{Guilherme Fran\c ca} 
has a BSc in physics, and received both his MSc and 
PhD in Theoretical Physics from the Institute of 
Theoretical Physics IFT-UNESP/ICTP-SAIFR (2012). He was a Postdoctoral Fellow
with the High Energy Theory group in the Physics Department 
at Cornell University (2013--2015), working on topics of mathematical physics
and non-perturbative methods in quantum field theory 
and statistical mechanics.
He was a Postdoctoral Fellow in
the Computer Science Department at Boston College (2015), working in
optimization theory.
Since 2016 he is a Postdoctoral Fellow at Johns Hopkins University, currently
with the Mathematical Institute for Data Science (MINDS). 
His current research interests are in theoretical methods in the broad
area of machine learning 
and optimization.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{Maria Rizzo}
Biography text here.
\end{IEEEbiographynophoto}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio]{gui2.png}}]{Guilherme Fran\c ca} 
has a BSc in physics, and received both his MSc and 
PhD in Theoretical Physics from the Institute of 
Theoretical Physics IFT-UNESP/ICTP-SAIFR (2012). He was a Postdoctoral Fellow
with the High Energy Theory group in the Physics Department 
at Cornell University (2013--2015), working on topics of mathematical physics
and non-perturbative methods in quantum field theory 
and statistical mechanics.
He was a Postdoctoral Fellow in
the Computer Science Department at Boston College (2015), working in
optimization theory.
Since 2016 he is a Postdoctoral Fellow at Johns Hopkins University, currently
with the Mathematical Institute for Data Science (MINDS). 
His current research interests are in theoretical methods in 
machine learning 
and optimization.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio,height=1.25in]{rizzo.jpg}}]{Maria Rizzo}
I hold a BS and MA degree in Mathematics from the University of Toledo, a MS in
Applied Statistics
from BGSU, and a PhD from BGSU in 2002. After four years as Assistant Professor
at Ohio University
Department of Mathematics, I returned to BGSU in 2006, where I am currently
Professor of Statistics in
the Department of Mathematics and Statistics. Primary research interests are
centered on energy statistics,
distance correlation and its applications, computational statistics, and
related topics. In addition
to teaching statistics, data science, and actuarial science, I enjoy writing
textbooks about
statistical computing and using R software, a forthcoming research monograph on
energy statistics
(joint with G. Szekely) and have other book writing projects under contract as
well.
\end{IEEEbiography}
